My title

### 2023-03-23 outputs/paper/paper.qmd
some editing

Around the time that Midnights came out, I came across a video on Twitter of a guy guessing which songs on Midnights were produced by Antonoff within seconds. The tweet reads: "im able to instantly detect if jack antonoff worked on a song due to a visceral hatred of his production style". He nails it. Only one song on the album wasn't produced by Antonoff, and he guesses it.

@@

6.  Which was further double down on when I found a screenshot he took of his Tweet drafts, one of which being: "people often say to me:"caleb, what's wrong with jack antonoff?". don't ask questions"

It is a perfect video essay. The only thing left I could ask was how he felt about that video 6 months after the fact, and what he thought of me asking him about it.

@@

Taste is subjective. People who can play instruments tend to be better at deciphering and describing sounds. Antonoff is everywhere. Cultural criticism is a hall of smoke and mirrors.

Can we translate any of this into something observable? Can be quantify the Jack Antonoff-ification of music?

>>>>

Around the time that Midnights came out, I came across a video on Twitter of a guy, Caleb Gamman, guessing which songs on Midnights were produced by Antonoff within seconds. The tweet reads: "im able to instantly detect if jack antonoff worked on a song due to a visceral hatred of his production style". He nails it. Only one song on the album wasn't produced by Antonoff, and he guesses it.

@@

6.  Which was further doubled down on when I found a screenshot he took of his Tweet drafts in June 2021, one of them reading: "people often say to me:"caleb, what's wrong with jack antonoff?". don't ask questions"

It is a perfect video essay. The only thing left that I could ask was how he felt about that video 6 months after the fact, and what he thought of me asking him about it.

@@

Taste is subjective. People who can play instruments tend to be better at identifying and describing sounds. Cultural criticism is a hall of smoke and mirrors. Antonoff is everywhere.

Can we translate any of this into something observable? Can we quantify the Jack Antonoff-ification of pop music?
